---
title: "Guide to phipcc for Larman Lab"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{larmanguide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction

[`phipcc`](https://github.com/brandonsie/phipcc) in an R package designed to generate R Markdown reports for case-control studies of [PhIP-seq](https://www.nature.com/articles/s41596-018-0025-6) data.

`phipcc` builds analysis targets using the [`drake`](https://github.com/ropensci/drake) package from rOpenSci and Will Landau.

Also depends on `phipmake`, `epitopefindr`, and `AVARDA`.

This guide is written specifically for the Larman Lab and MARCC. Eventually I will write a more general guide.

# Overview

There are two major phipcc functions that the user will interact with.  

* `phipcc::define_plan_case_control()` defines the computational case control plan to be executed by `drake::make()`. This function `define_plan_case_control` reads configuration settings from `config.tsv`, which will be discussed in depth in a later section of this guide.  
* `phipcc::render_from_template()` reads in outputs from the case control plan and uses an R Markdown template to generate an HTML report. (the default template is provided in the package `system.file("template_case_control.Rmd", package = "phipcc")`, but custom templates can also be used.)  

Currently, `define_plan_case_control()` and the subsetquent call to `drake::make()` can be run on MARCC. However, the final step of knitting the final report depends on `pandoc`, a dependency that I haven't yet figured out how to get working on MARCC. However, you can copy the necessary files to your local computer and run `render_from_template` locally.

# Software Setup

## MARCC

```{bash, eval = FALSE}

cd /data/hlarman1/PhIPdb/Software/install_r_pkg
sbatch --export=pkg="brandonsie/drake" installGithub.sh
sbatch --export=pkg="brandonsie/phipmake" installGithub.sh
sbatch --export=pkg="brandonsie/phipcc" installGithub.sh

# Epitopefindr-specific setup
sbatch --export=pkg="brandonsie/epitopefindr" installGithub.sh
sbatch --export=pkg="mhahsler/rBLAST" installGithub.sh
sbatch --export=pkg="brandonsie/pdfuniter" installGithub.sh
sbatch --export=pkg="Biostrings" installBioc.sh
sbatch --export=pkg="IRanges" installBioc.sh
sbatch --export=pkg="msa" installBioc.sh
sbatch --export=pkg="S4Vectors" installBioc.sh

```

## Local

Install [R (e.5+)](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/). 
In R console, execute:

```{r, eval = FALSE}

# Required (for steps that are not yet supported on MARCC)
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("brandonsie/phipcc")
install.packages("pdftools")

# Optional (for steps that can be carried out either locally or on MARCC)
remotes::install_github("ropensci/drake")
remotes::install_github("brandonsie/phipmake")
remotes::install_github("brandonsie/epitopefindr")
remotes::install_github("mhahsler/rBLAST")
remotes::install_github("brandonsie/pdfuniter")
if (!requireNamespace("BiocManager")) install.packages("BiocManager")
BiocManager::install(c("Biostrings", "IRanges", "msa", "S4Vectors"))

```

## Note

`epitopefindr` also depends on [BLAST+](https://blast.ncbi.nlm.nih.gov/Blast.cgi?PAGE_TYPE=BlastDocs&DOC_TYPE=Download) and `pdflatex` e.g. from [TeX Live](https://www.tug.org/texlive/). I have already installed these for the Larman Lab group on MARCC. From the Larman Lab group MARCC, installations can be sourced by entering:

```{bash, eval = FALSE}
export PATH=/data/hlarman1/PhIPdb/Software/texlive/2018/bin/x86_64-linux:"$PATH"
export PATH=/data/hlarman1/PhIPdb/Software/BLAST+/ncbi-blast-2.8.1+/bin:"$PATH"

```



# Preparing a Case-Control Study

## Prerequisites

`phipcc` assumes that the `phipmake` pipeline including `AVARDA` has already been run on the data for your case and control samples.

## Configuration File

A template is provided with field descriptions. In R, you can access this template by running `file.copy(system.file("example_config.tsv", package = "phipcc"), "config.tsv")`. For now, you will need to edit fields manually.

### Description of Each Field


## MARCC `phipcc`/`drake` pipeline

```{bash, eval = FALSE}

cd /data/hlarman1/PhIPdb/Software/phipcc
 wd=~/data/PhIPdb/Studies/Brandon/CaseControl/Lupus/virscan/
 sbatch --export=wd=$wd runphipcc.sh

```

## Local report knitting

Enable view hidden folders, then copy ".drake" and "data/" to a new project folder.
Locally from RStudio, 
```{r, eval = FALSE}

setwd("new_project_folder")
phipcc::render_from_template()

```

