---
author: "Brandon Sie"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: inline
params:
  set_title: "Test"
  config: NULL
  candidate_table_flagged: NULL
  candidate_table_full: NULL
  graphs: NULL
  cluster1: NULL
  motifs: NULL
  cluster2: NULL
title: "`r params$set_title`"
---


# I. Introduction {.tabset}

## Report Overview  

This report compares the data of our case population (__`r phipmake::getparam(config, "proj_id")`, n = `r phipmake::getparam(config, "case_names") %>% strsplit(phipmake::getparam(config, "delimiter")) %>% unlist %>% length`__)
against that of a control population (__`r phipmake::getparam(config, "ctrl_id")`, n = `r phipmake::getparam(config, "ctrl_names") %>% strsplit(phipmake::getparam(config, "delimiter")) %>% unlist %>% length`__)
to generate a list of candidate antigens from the __`r phipmake::getparam(config, "library")`__ library.

## Navigating this Document  

* Table of Contents on the Left  
* Interactive Plots  
* Folded Code  
* Tabbed section  

## Config Documentation  

```{r Config Documentation}

knitr::kable(config) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = TRUE) %>% 
  kableExtra::column_spec(2, width = "10em")

```


# II. Candidate Antigen Tables {.tabset}  
<font size="1"><a href="#top">[Top]</a></font>  

From a BH-corrected Fisher's Exact test.

## Annotated  
Known associations in our database. (e.g. autoantigens, surface proteins, ...)  
```{r Candidate Table 1}


border <- "1px solid gray"
scroll_height <- "1000px"
use_scrollbox <- FALSE

flag_table <- params$candidate_table_flagged
if(nrow(flag_table) > 17) use_scrollbox <- TRUE

flag_table <- flag_table %>%
    knitr::kable(
      format = "html", escape = FALSE,
      caption = "Annotated Candidate Antigens", row.names = FALSE) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = TRUE) %>% 
    kableExtra::add_header_above(
      c(" " = 4, "Hit Freq" = 2,"Median Hit Score" = 2," " = 1)) %>%
     kableExtra::column_spec(1,border_left = border) %>%
     kableExtra::column_spec(ncol(flag_table), border_right = border) %>%
     kableExtra::column_spec(c(1:4,6,8), border_right = border) 

if(use_scrollbox){
  flag_table <- flag_table %>% kableExtra::scroll_box(height = scroll_height)
}

flag_table

```

## All Hits  
```{r Candidate Table 2}


full_table <- params$candidate_table_full
if(nrow(full_table) > 17) use_scrollbox <- TRUE

  # (!) add this to markdown report
  # (!) kable is knitr. specify other functions too

full_table <- full_table %>%
    knitr::kable(
      format = "html", escape = FALSE,
      caption = "All Candidate Antigens", row.names = FALSE) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = TRUE) %>% 
    kableExtra::add_header_above(
      c(" " = 4, "Hit Freq" = 2,"Median Hit Score" = 2," " = 1)) %>%
     kableExtra::column_spec(1,border_left = border) %>%
     kableExtra::column_spec(ncol(full_table), border_right = border) %>%
     kableExtra::column_spec(c(1:4,6,8), border_right = border)

if(use_scrollbox){
  full_table <- full_table %>% kableExtra::scroll_box(height = scroll_height)
}

full_table

```



# III. Exploratory Analysis {.tabset}    
<font size="1"><a href="#top">[Top]</a></font>  


## Hit Frequency vs. Hit Score in Cases
```{r Plot 1}
plotly::ggplotly(graphs[[1]])
```

##  Median Hit Score, Cases vs. Controls
```{r Plot 2}
plotly::ggplotly(graphs[[2]])
```

## P-Value vs. Median Case Hit Score
```{r Plot 3}
plotly::ggplotly(graphs[[3]])
```



# IV. Hit Clustering {.tabset}  
<font size="1"><a href="#top">[Top]</a></font>  

## Clustergram

```{r Clustergram 1, fig.width = 9, fig.height = 9}
clustergram_sorted <- params$cluster1[[3]]
ncolors <- 2
my_palette <- colorRampPalette(c("white","black"))(n = ncolors)


 heatmaply::heatmaply(
    clustergram_sorted,
    main = paste("Candidate Antigen Clustergram"),
    colors = my_palette,
    fontsize_row = 8,
    fontsize_col = 8,
    column_text_angle = 90,
    margins = c(65, 120),
    trace = "both",
    tracecol = "grey",
    Rowv = FALSE,
    Colv = FALSE,
    grid_gap = 1,
    hide_colorbar = TRUE)
 
```


## Row (Peptide) Dendrogram
```{r Row Dendrogram 1, fig.width = 9, fig.height = 9}
row_dendrogram <- params$cluster1[[1]]$rowDendrogram

g <- ggdendro::ggdendrogram(row_dendrogram, rotate = TRUE) + 
  ggplot2::theme(axis.text.y = element_text(size = 8)) 
plotly::ggplotly(g)

```

## Column (Sample) Dendrogram
```{r Col Dendrogram 1, fig.width = 9, fig.height = 9}
col_dendrogram <- params$cluster1[[1]]$colDendrogram

g <- ggdendro::ggdendrogram(col_dendrogram, rotate = TRUE) + 
  ggplot2::theme(axis.text.y = element_text(size = 8)) 
plotly::ggplotly(g)

```


# V. Epitope Clustering   
<font size="1"><a href="#top">[Top]</a></font>  

## epitopefindr Motifs {.tabset}  
Ran epitopefinder, got these motifs
<!-- (!) Also need to print output table  -->

```{r Print Motifs, fig.height = 4, echo = FALSE, message = FALSE, results = "asis"}

#print precomputed motifs
# msa_path <- "data/epitopefindr/intermediate_files/msa/"
msa_path <- params$motifs
msa_name <- paste0(msa_path, "msa.pdf")
num_page <- pdftools::pdf_info(msa_name)$pages
num_length <- nchar(num_page)

for(i in 1:num_page){
  num_padded <- formatC(i, width = num_length, flag = "0")
  png_name <- paste0(msa_path, "msa-", num_padded, ".png")

  		cat("  \n### MSA",  i, "  \n")
		for(j in 1:length(png_name)){
  		cat("![](",png_name[j],")",sep="")
		  # png_name[j] %>% (EBImage::readImage) %>% (EBImage::display)
		}
		cat("  \n  \n")


}


```


## Epitope-Collapsed Hit Clustering {.tabset}

### Epitope Clustergram
```{r Clustergram 2, fig.width = 9, fig.height = 9}
clustergram_sorted <- params$cluster2[[3]]
ncolors <- 2
my_palette <- colorRampPalette(c("white","black"))(n = ncolors)


 heatmaply::heatmaply(
    clustergram_sorted,
    main = paste("Candidate Antigen Clustergram (Epitope-Collapsed)"),
    colors = my_palette,
    fontsize_row = 8,
    fontsize_col = 8,
    column_text_angle = 90,
    margins = c(65, 120),
    trace = "both",
    tracecol = "grey",
    Rowv = FALSE,
    Colv = FALSE,
    grid_gap = 1,
    hide_colorbar = TRUE)

```

### Row (Peptide/Epitope) Clustergram
```{r Row Dendrogram 2, fig.width = 9, fig.height = 9}
row_dendrogram <- params$cluster2[[1]]$rowDendrogram

g <- ggdendro::ggdendrogram(row_dendrogram, rotate = TRUE) + 
  ggplot2::theme(axis.text.y = element_text(size = 8)) 
plotly::ggplotly(g)

```


### Column (Sample) Clustergram
```{r Col Dendrogram 2, fig.width = 9, fig.height = 9}
col_dendrogram <- params$cluster2[[1]]$colDendrogram

g <- ggdendro::ggdendrogram(col_dendrogram, rotate = TRUE) + 
  ggplot2::theme(axis.text.y = element_text(size = 8)) 
plotly::ggplotly(g)

```



<!-- 
Pass whole precomputed tables as params
specify libraries



https://stackoverflow.com/questions/30377213/how-to-include-rmarkdown-file-in-r-package/30377598
put rmd in inst
installed inst goes to main directory
after build/install, reference with 
system.file("template_case_control.Rmd", package="phipcc")
"C:/Users/Brandon/Documents/R/win-library/3.5/phipcc/template_case_control.Rmd"
-->